Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2020-05-06 manuscript/manuscript.tex
ms updates

\begin{align}
  \vb{G(t) = \frac{ \sum_{i=0}^{t-1} \sum_{j \ne i}^{t-1} \cov(\Delta p_i, \Delta p_j)}{\var(p_t - p_0)}}
\end{align}
%
which estimates the effect of selection on allele frequency change between the
initial generation $0$ and some later generation $t$, which can be varied to
see how this quantity grows through time. Since \textcite{Barghi2019-qy}
experiment is sequenced every ten generations, in the numerator for the
covariance we use the allele frequency changes between adjacent timepoints,
which are ten generations apart; \vb{thus the strong covariances between
  adjacent generations are not observable and do not contribute to the
  numerator of $G(t)$}. \vb{Additionally, selection also inflates the variance
  in allele frequency change per generation; however, this effect cannot be
  easily distinguished from drift.} \vb{For both these reasons, our measure
  $G(t)$ is strongly conservative} (\vb{we demonstrate this through simulations
in Supplementary Material Section \ref{supp:tempblocks}}). Still, we find a
remarkably strong signal. Greater than $20\%$ of total, genome-wide allele
frequency change over 60 generations is the result of selection (Figure
\ref{fig:figure-1} B).

>>>>

\begin{align}
  \vb{G(t) = \frac{ \sum_{i=0}^{t-1} \sum_{j \ne i}^{t-1} \cov(\Delta p_i, \Delta p_j)}{\var(p_t - p_0)}}
\end{align}
%

which estimates the \vb{impact of selection} on allele frequency change between
the initial generation $0$ and some later generation $t$, which can be varied
to see how this quantity grows through time. \vb{This measure can intuitively
  be understood as the relative fraction of allele frequency change normally
  thought of as ``drift" that is actually due to selection; the denominator of
  $G(t)$ is $\var(p_t - p_0)$, which under drift alone is proportional to
  $\nicefrac{1}{2 N_e}$. By measuring the contribution of temporal covariances
caused by selection, $G(t)$ looks at the fraction selection contributes to what
looks like a faster rate of drift, or lower $N_e$.} Since
\textcite{Barghi2019-qy} experiment is sequenced every ten generations, in the
numerator for the covariance we use the allele frequency changes between
adjacent timepoints, which are ten generations apart; \vb{thus the strong
  covariances between adjacent generations are not observable and do not
  contribute to the numerator of $G(t)$}. \vb{Additionally, selection also
  inflates the variance in allele frequency change per generation; however,
  this effect cannot be easily distinguished from drift.} \vb{For both these
reasons, our measure $G(t)$ is strongly conservative} (\vb{we demonstrate this
through simulations in Supplementary Material Section \ref{supp:tempblocks}}).
Still, we find a remarkably strong signal. Greater than $20\%$ of total,
genome-wide allele frequency change over 60 generations is the result of
selection (Figure \ref{fig:figure-1} B).
